Factor Analysis on Report Citations, using a Combined Latent and logistic Model

### 2019-05-13 manuscript.tex
Fourth Update

\documentclass{article}
\usepackage{mathtools}
\usepackage[nottoc]{tocbibind}
\usepackage[nohead, nomarginpar, margin=1in, foot=.25in]{geometry}
\usepackage{mathtools}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage{float}  % For fixing the image in draft

\usepackage{amsmath}
\usepackage{lscape} 
\usepackage{graphicx}
\graphicspath{ {./images/} }

%\usepackage{nips10submit_e}
\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
%\usepackage{epstopdf}
\usepackage{natbib}
%\usepackage{mathbbold}
\usepackage{bm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{array}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{property}[theorem]{Property}
\newtheorem{result}[theorem]{Result}
\newtheorem{example}[theorem]{Example}

\newtheorem*{remark*}{Remark}
\DeclareGraphicsExtensions{.eps}

\renewcommand{\baselinestretch}{1} % 2.0 or 3.0 would do.
\renewcommand*\labelenumi{(\theenumi)}
\renewcommand\theequation{\arabic{section}.\arabic{equation}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[linesnumbered,ruled]{algorithm2e}
\RestyleAlgo{boxruled}

\topmargin 0pt \advance \topmargin by -\headheight \advance \topmargin by
-\headsep \textheight 8.9in \oddsidemargin 0pt \evensidemargin
\oddsidemargin \marginparwidth 0.5in \textwidth 6.5in

\begin{document}
\title{Factor Analysis on Report Citations, Using a Combined Latent and logistic Model}
\author{Namjoon Suh, Xiaoming Huo, Eric Heim, Timothy Van Slyke, and Lee Seversky}

\date{\today}
\maketitle

\begin{abstract}
% To be added later...
We propose a combined latent and logistic model for the citation network, where either a latent model or a logistic model alone is often insufficient to capture the structure of the data.
    The proposed model has a latent (i.e., factor analysis) model to represents the main technological trends (aka factors), and adds a sparse logistic component that captures the remaining ad hoc dependence. Parameter estimation are carried out through construction of a joint-likelihood function of edges and properly chosen penalty terms. The convexity of the likelihood function allows us to develop an efficient algorithm, while the penalty terms generate a low-dimensional latent component and a sparse graphical structure. Simulation results are reported that show the new method works well in practical situations. The proposed method has been applied to a real application in citation network of statistician data set (Ji and Jin, 2016 \cite{ji2016coauthorship}).
\end{abstract}

\noindent{\sc KEY WORDS}: citation network, matrix decomposition, latent variable model,  logistic model, convex optimization

@@

\bibliographystyle{plain}
\bibliography{references.bib}

>>>>

\documentclass[AMS,STIX1COL]{WileyNJD-v2}
%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
%\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{float}  % For fixing the image in draft
\usepackage{lscape} 
%\usepackage[nottoc,notlot,notlof]{tocbibind}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\articletype{Article Type}%

\received{13 May 2019}
\revised{13 May 2019}
\accepted{13 May 2019}

\raggedbottom

\begin{document}

\title{Factor Analysis on Report Citations, using a Combined Latent and logistic Model}

\author[1]{Namjoon Suh*}

\author[1]{Xiaoming Huo}

\author[3]{Eric Heim}

\author[3]{Timothy Van Slyke}

\author[3]{Lee Seversky}

\authormark{AUTHOR ONE \textsc{et al}}

\address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}

\presentaddress{This is sample for present address text this is sample for present address text}

\abstract[Summary]{We propose a combined latent and logistic model for the citation network, where either a latent model or a logistic model alone is often insufficient to capture the structure of the data. The proposed model has a latent (i.e., factor analysis) model to represents the main technological trends (aka factors), and adds a sparse logistic component that captures the remaining ad hoc dependence. Parameter estimation are carried out through construction of a joint-likelihood function of edges and properly chosen penalty terms. The convexity of the likelihood function allows us to develop an efficient algorithm, while the penalty terms generate a low-dimensional latent component and a sparse graphical structure. Simulation results are reported that show the new method works well in practical situations. The proposed method has been applied to a real application in citation network of statistician data set (Ji and Jin, 2016 \cite{ji2016coauthorship}).
}

\keywords{citation network, matrix decomposition, latent variable model,  logistic model, convex optimization}

\jnlcitation{\cname{%
\author{Williams K.}, 
\author{B. Hoskins}, 
\author{R. Lee}, 
\author{G. Masato}, and 
\author{T. Woollings}} (\cyear{2016}), 
\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}

\maketitle

\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

@@

\nocite{*}
\bibliography{References}%

%\backmatter
